Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-10-23 manuscript/bef_stability/manuscript.Rmd
Fix figure label reference in main text

- Number of words:
  - Abstract: 172
  - Main text: 4929

- Number of references: XXX
- Number of figures: 2
- Number of tables: 1
- Number of text boxes: 0

@@

```{r matmet, fig.cap = matmet_cap, results = "fig.show"}
library(knitr)
include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
```

@@

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) C), then (2) determine network of a given community by
extracting the metaweb according to the trophic species present at a given
site and sampling event (Figure \@ref(fig:matmet) D).

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae and fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, than species [@jennings_weak_2001].

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. Species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (cf Bonnaffe ref). Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

@@

Structural Equation Modeling enables us to assess multivariate relationships
between variables. It is a promising way to go beyond bivariate relationships
and to investigate complex relationships, direct and
indirect, between variables [@grace_structural_2008; @grace_causal_2014;
@lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
model explaining the annual total biomass allowed the environment
to affect directly species richness and network structure, as well as annual total
biomass (Figure \@ref(fig:sem-plot) B). We assumed that both species richness
and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
B) and that species richness affected foodweb structure
[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].

We used the same model structure for temporal stability of biomass (Figure
\@ref(fig:sem-plot) A). Instead of the annual total biomass, we modelled the
synchrony and population variability which in turn determined the temporal
stability of biomass. The structural equation models used for annual total
biomass and its temporal stability contained respectively 4 and 6 response
variables, 35 and 26 direct paths.

@@

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for (A) biomass stability and
  (B) total biomass. ",
  "Results of the Structural Equation Models for (C) the
  determinants of biomass stability and (D) total biomass. Red and green arrows
  represent respectively negative and positive path coefficients. The path
  coefficients are standardized. For convenience, only significant
  paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
  second axis of the PCA."
)
```

@@

The structural equation models explained a large part of the variation
of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
.45$, $.47$, $.49$ and $.38$) but less so for mean trophic level ($R^2 =
.18$, Figure \@ref(fig:sem-plot) C and D). We found that species richness had a
significant negative effect on mean trophic level ($r_\delta = 
`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_stab$total`$, Figure
\@ref(fig:sem-plot) C and D), meaning that a part of the effects of species richness went 
through network structure.

@@

Species richness and mean trophic level had a significant positive direct effect
on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
$r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) D, Table
\@ref(tab:indir-sem)),
while connectance had no direct effect on total biomass (Figure
\@ref(fig:sem-plot) D).

@@

By its effects on synchrony and $\overline{CV_{sp}}$, species richness had a
negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
Table \@ref(tab:indir-sem)). This effect resulted from two opposite effects. On
the one hand, species richness had a direct negative effect on synchrony
($r_\delta = `r rich_on_sync$direct`$), thereby
increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
hand, species richness had a positive direct effect on $\overline{CV_{sp}}$
($r_\delta = `r rich_on_cv_sp$direct`$),
thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
\@ref(tab:indir-sem)). The negative effect of $\overline{CV_{sp}}$ on temporal
stability was twice higher than the negative effect of synchrony (resp.
$r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Figure
\@ref(fig:sem-plot) C).

The total effect of mean trophic level on temporal stability of biomass was of
the same magnitude than the one of species richness (resp.
$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
\@ref(tab:indir-sem)).
The mean trophic level had only a direct negative effect on
$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
Figure \@ref(fig:sem-plot) C) and thereby had a total positive
effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
(Figure \@ref(fig:sem-plot) C, Table \@ref(tab:indir-sem)).

@@

The average trophic level was positively linked to total biomass.
Experimental and theoretical work suggested that a higher trophic level is the
result of a stronger top-down effect, meaning higher predation rates and biomass
fluxes to higher trophic levels [@kratina_warming_2012], hence leading to an
increase in total biomass with trophic length. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increase
with the length of trophic chains and so results in higher total biomass.

>>>>

- Number of words:
  - Abstract: 172
  - Main text: 5383

- Number of references: 87 
- Number of figures: 2
- Number of tables: 1
- Number of text boxes: 0

@@

```{r matmet, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
library(knitr)
include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"),)
```

@@

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) B), then (2) determine network of a given community by
extracting the metaweb according to the trophic species present at a given
site and sampling event (Figure \@ref(fig:matmet) C and D).

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae and fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) B, C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, than species [@jennings_weak_2001].

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. Species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature [REF WILLEM]. Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

@@

Structural Equation Modeling enables us to assess multivariate relationships
between variables. It is a promising way to go beyond bivariate relationships
and to investigate complex relationships, direct and
indirect, between variables [@grace_structural_2008; @grace_causal_2014;
@lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
model explaining the annual total biomass allowed the environment
to affect directly species richness and network structure, as well as annual total
biomass (Figure \@ref(fig:sem-plot) A). We assumed that both species richness
and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
A) and that species richness affected foodweb structure
[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].

We used the same model structure for temporal stability of biomass (Figure
\@ref(fig:sem-plot) C). Instead of the annual total biomass, we modelled the
synchrony and population variability which in turn determined the temporal
stability of biomass. The structural equation models used for annual total
biomass and its temporal stability contained respectively 4 and 6 response
variables, 35 and 26 direct paths.

@@

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for the (A) median of annual
  total biomass (in grams by square meter) and (C) its temporal stability.",
  "Results of the Structural Equation Models for
  (B) the determinants of the median of annual total biomass and (D) its temporal stability. Red and green
  arrows represent respectively negative and positive path coefficients. The
  path coefficients are standardized. For convenience, only significant
  paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
  second axis of the PCA."
)
```

@@

The structural equation models explained a large part of the variation
of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
.45$, $.47$, $.49$ and $.38$) but less so for mean trophic level ($R^2 =
.18$, Figure \@ref(fig:sem-plot) B and D). We found that species richness had a
significant negative effect on mean trophic level ($r_\delta = 
`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_stab$total`$, Figure
\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
through network structure.

@@

Species richness and mean trophic level had a significant positive direct effect
on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
$r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) B, Table
\@ref(tab:indir-sem)),
while connectance had no direct effect on total biomass (Figure
\@ref(fig:sem-plot) B).

@@

By its effects on synchrony and $\overline{CV_{sp}}$, species richness had a
negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
Table \@ref(tab:indir-sem)). This effect resulted from two opposite effects. On
the one hand, species richness had a direct negative effect on synchrony
($r_\delta = `r rich_on_sync$direct`$), thereby
increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
hand, species richness had a positive direct effect on $\overline{CV_{sp}}$
($r_\delta = `r rich_on_cv_sp$direct`$),
thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
\@ref(tab:indir-sem)). The negative effect of $\overline{CV_{sp}}$ on temporal
stability was twice higher than the negative effect of synchrony (resp.
$r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Figure
\@ref(fig:sem-plot) D).

The total effect of mean trophic level on temporal stability of biomass was of
the same magnitude than the one of species richness (resp.
$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
\@ref(tab:indir-sem)).
The mean trophic level had only a direct negative effect on
$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
Figure \@ref(fig:sem-plot) D) and thereby had a total positive
effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
(Figure \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)).

@@

The average trophic level was positively linked to total biomass.
Experimental and theoretical work suggested that a higher trophic level can be the
result of a stronger top-down effect, meaning higher predation rates and biomass
fluxes to higher trophic levels [@kratina_warming_2012], hence leading to an
increase in total biomass with trophic length. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increase
with the length of trophic chains and so results in higher total biomass.
